The pollination trade-off

### 2018-02-28 publication/supp_info.Rmd
Do not show deposited plant boxplots. They are ugly

```{r fig-conspecific-per-site, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })

@@

```{r fig-conspecific-per-plant, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })

>>>>

```{r fig-conspecific-per-site, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across plant species for different communities. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio."}
loadd(dep_frame, sites)
site_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>% 
  plyr::dlply('site_name', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = recipient_short,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() + 
      ggtitle(paste(x$locality[1], '-', x$land_use, x$fragment)) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })

@@

```{r fig-conspecific-per-plant, eval = FALSE, fig.height = 7, fig.cap="Conspecific pollen density across communities for different study species. Only species present in more than onse site are shown. Community names are abbreviated: AN stands for Anquilóo, LC for Las Chiclas, and SC for San Claudio; A, and R indicate that the community corresponded to an agricultural or reserve site respectively."}
loadd(dep_frame, sites)
plant_plots_conspecific <- dep_frame %>%
  filter(pollen_category == 'conspecific') %>%
  inner_join(sites, by = 'site_name') %>%
  mutate(recipient_short = shorten_sp_name(recipient)) %>%
  mutate(pollen_category = paste(pollen_category, "pollen"), 
         treatment = if_else(treatment == 'closed', 'bagged', treatment)) %>%
  group_by(recipient) %>%
  mutate(n_sites = n_distinct(site_name), 
         site_name = `str_sub<-`(site_name, 1, 3, value = ''), 
         site_name = str_replace_all(site_name, '_', ' - ')) %>%
  group_by() %>%
  filter(n_sites >= 2) %>%
  plyr::dlply('recipient', function(x){
    x %>%
      ggplot(aes(y = pollen_density + 1, x = site_name,
                 fill = treatment)) +
      geom_boxplot(size = 0.25, outlier.size = 0.5, outlier.stroke = 0.5) +
      scale_y_log10(breaks = c(10,100,1000)) +
      coord_flip() +
      ggtitle(paste(x$recipient[1])) +
      pub_theme() +
      xlab(NULL) +
      ylab('pollen density') +
      scale_fill_brewer(palette = "Set1")
  })
